better title eventually

### 2015-05-11 cs261n-paper/paper.tex
finished reddening all unfinished sections and inline comments.

\section{UX sprint} 
\label{sec:pilot}
Details. Gory gory details of how it all went down. 
Include the recruitment process, the setup, what the exact 
tasks were for participants, demographics, everything. 
It all should have a home here.

\subsection{Motivation}
Talk about why we did what we did, and what the end goal 
of the experiment was. Also talk about how we expected users
to be much better at installing and downloading than they were.

\subsection{Experiment Overview}
Talk about how the experiment was for an average user. We start
with the cognitive walkthrough, then have them do one on a dummy
and calibration task, we give feedback on the walkthrough, and then 
give them the freedom to complete the web tasks.

{\color {red}  GET THE LIST OF TASKS WE MADE THEM DO.}

\subsection{Methodology}
How we recruited, what the setup was like, how we got the tasks, details of 
how the experiment was run, and things like that.

\subsection{Results}
Present situations which really were unexpected. 
Also extract the golden quotes and state them here 
to prove points I want to make.

@@

\subsection{Impact}
whoo talk about the cool stuff that happened next here. 
This means talking about the tickets and changes made 
to the Tor browser, the start of a user manual, and 
increased Tor UX efforts as a whole.

>>>>

\section{UX sprint} 
\label{sec:pilot}
 {\color {red}Details. Gory gory details of how it all went down. 
Include the recruitment process, the setup, what the exact 
tasks were for participants, demographics, everything. 
It all should have a home here.}

\subsection{Motivation}
{\color {red} Talk about why we did what we did, and what the end goal 
of the experiment was. Also talk about how we expected users
to be much better at installing and downloading than they were. }

\subsection{Experiment Overview}
{\color {red} Talk about how the experiment was for an average user. We start
with the cognitive walkthrough, then have them do one on a dummy
and calibration task, we give feedback on the walkthrough, and then 
give them the freedom to complete the web tasks.

GET THE LIST OF TASKS WE MADE THEM DO.}

\subsection{Methodology}
{\color {red} How we recruited, what the setup was like, how we got the tasks, details of 
how the experiment was run, and things like that.}

\subsection{Results}
{\color {red} Present situations which really were unexpected. 
Also extract the golden quotes and state them here 
to prove points I want to make. }

@@
